Modularizing Street Map Generation \\ \vspace{8pt} \large An Adventure in Tensors

### 2013-12-12 paper/paper.tex
improved cycle detection figure

\documentclass[twocolumn]{article}
\usepackage{amsmath}
\usepackage{graphicx}

@@

\todo{insert pipeline diagram}

@@

\subsection{Eigenvectors}
The eigenvalues of a tensor $t$ represented by the matrix $\sqmat{a}{b}{b}{-a}$
are:
\[
    \lambda = \pm\sqrt{a^2+b^2} \\
\]
The major eigenvalue, $\lambda_1$, is the larger value, and the minor
eigenvalue, $\lambda_2$ is the smaller value. The corresponding eigenvectors
are then
\[
    \epsilon_i = \left\{1,\frac{\lambda_i-a}{b}\right\}
\]
The eigenvectors are defined if the tensor field is not degenerate (that is,
$a$ and $b$ are both zero) at that point.

@@

\todo{image of that nice circular constraint that worked really well with this}

@@

\todo{death spiral and improved version}

@@

\todo{add practical results of this method if we can get it working}

>>>>

\documentclass[twocolumn]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subcaption}

@@

\begin{figure*}[t!]
\todo{reimplement pipeline image in \LaTeX}
\begin{center}
    \includegraphics[width=5.5in]{images/pipeline.pdf}
\end{center}
\caption{Overview of our pipeline}
\label{fig:pipeline}
\end{figure*}

@@

\subsection{Eigenvectors}
The eigenvalues of a tensor $t$ represented by the matrix $\sqmat{a}{b}{b}{-a}$
are:
\[
    \lambda = \pm\sqrt{a^2+b^2} \\
\]
The major eigenvalue, $\lambda_1$, is the larger value, and the minor
eigenvalue, $\lambda_2$ is the smaller value. The corresponding eigenvectors
are then
\[
    \epsilon_i = \left\{1,\frac{\lambda_i-a}{b}\right\}
\]
The eigenvectors are defined if the tensor field is not degenerate (that is,
$a$ and $b$ are both zero) at that point \cite{find-evs}.

@@

\begin{figure*}[t!]
    \todo{image of that nice circular constraint that worked really well with this}
\caption{Haskell implementation of eigenvector calculation}
% \label{fig:cycles} name?
\end{figure*}

@@

\floatstyle{plain}
\restylefloat{figure}
\begin{figure*}[t!]
    \centering
    \begin{subfigure}[b]{2.4in}
        \fbox{\includegraphics[width=\textwidth]{images/cycle_nodetection.pdf}}
        \caption{without cycle detection}
    \end{subfigure}
    \hspace{20pt}
    \begin{subfigure}[b]{2.4in}
        \fbox{\includegraphics[width=\textwidth]{images/cycle_detection.pdf}}
        \caption{with cycle detection}
    \end{subfigure}
\caption{Streamline tracing cycle detection}
\label{fig:cycles}
\end{figure*}
\floatstyle{boxed}
\restylefloat{figure}

@@
